Add Data

### 2025-02-10 data.qmd
Remove tinytable
tinytable is a lightweight package
but we don't even need it. The
data dictionary can be exported
to markdown using datawizard alone.
Also, we use datawizard::data_select
rather than base::subset to keep
the attributes of the data.frame.

Whether or not distributing the data set,
it is important to document the meaning (e.g., units)
and values of its variables.
This is typically done with a _data dictionary_ (also called a _codebook_).
In the following, we will demonstrate how to create a simple data dictionary
using the R packages [`datawizard`][datawizard] and [`tinytable`][tinytable].
You can install them now using:

[datawizard]: https://easystats.github.io/datawizard/
[tinytable]: https://vincentarelbundock.github.io/tinytable/

```{.r filename="Console"}
renv::install(c(
  "datawizard",
  "tinytable"
))
```

@@

Next, you can use `datawizard` again to create
the data dictionary containing the descriptions,
but also some other information about each variable
(e.g., the number of missing values).
Finally, you can use `tinytable` to print the table.

::: {.column-margin}
![tinytable: Simple and Configurable Tables](images/tinytable.svg){width=250px}
:::

@@

```{r}
#| echo: false
#| column: "body-outset"

(dict <- datawizard::data_codebook(dat) |>
  subset(select = -c(ID, .row_id)) |>
  tinytable::tt() |>
  tinytable::format_tt(replace = "")) # hide NAs
```

>>>>

Whether or not distributing the data set,
it is important to document the meaning (e.g., units)
and values of its variables.
This is typically done with a _data dictionary_ (also called a _codebook_).
In the following, we will demonstrate how to create a simple data dictionary
using the R package [`datawizard`][datawizard].
You can install them now using:

[datawizard]: https://easystats.github.io/datawizard/

```{.r filename="Console"}
renv::install("datawizard")
```

@@

Then, you can create the data dictionary containing the descriptions,
but also some other information about each variable
(e.g., the number of missing values) and print it.

@@

```{r}
#| echo: false
#| column: "body-outset"
#| classes: plain

datawizard::data_codebook(dat) |>
  datawizard::data_select(exclude = c("ID", ".row_id")) |>
  datawizard::data_filter(N != "") |>
  datawizard::print_md()
```
